---
title: "James Bond Film Analysis"
author: "Zihui Zhao"
format: html
---
```{r}
library(tidyverse)
bond.data <- read_csv("data/jamesbond.csv")
bond.data
```

## Which movie earned the most?
```{r}
bond.data |>
    select(Year, Movie, US_Gross) |>
    arrange(desc(US_Gross))
top_movie <- bond.data |>
    arrange(desc(US_Gross)) |>
    slice(1)
```
  The movie with the highest US box-office gross was `r top_movie$Movie`, released in `r top_movie$Year`. It earned about \$`r round(top_movie$US_Gross)` million at the US box office.

## Is there a correlation between budget and earnings?
```{r}

ggplot(bond.data, aes(x=Budget, y=US_Gross)) +
    geom_point()
```

 This doesn't account for inflation. Check: add colours for year?
```{r}
ggplot(bond.data, aes(x=Budget, y=US_Gross, color=Year)) +
    geom_point() +
    scale_color_continuous()
```
 Definitely looks like year correlates with both earnings and budget.
 The dataset contains inflation-adjusted numbers, let's use those instead.

```{r}
ggplot(bond.data, aes(x=Budget_Adj, y=US_Adj, color=Year)) +
    geom_point() +
    scale_color_continuous()
```

 Still seems budget is increasing with year even after inflation adjustment, but the correlation with returns is now much less clear.

## is there a correlation between the number of times Bond says "Bond, James Bond" and return??
```{r}
ggplot(bond.data, aes(x=BJB, y=US_Adj)) +
    geom_point() +
    scale_color_continuous()
```

 It seems the movies earn more if he says it 0 or 2 times?
 Probably a spurious correlation!


